%-------------------------
% Resume in Latex
% Author : Rakshit Kumar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
\input{glyphtounicode}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedright

\RequirePackage{xcolor}
\definecolor{cvblue}{HTML}{0E5484}
\definecolor{myblack}{HTML}{130810}     % renamed from 'black' to 'myblack' to avoid conflicts
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}

\colorlet{name}{myblack}                 % updated to use myblack
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{myblack}\titlerule \vspace{-5pt}]  % use myblack here as well

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}  
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}  
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}  
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
  {\Huge \scshape RAKSHIT KUMAR} \\ \vspace{1pt}
  Patna, Bihar \\ \vspace{1pt}
  \small
  \href{tel:+917091656096}{\faPhone\ +91 7091656096} ~
  \href{mailto:rakshitkumar.5905@gmail.com}{\faEnvelope\ rakshitkumar.5905@gmail.com} ~
  \href{https://linkedin.com/in/rakshit-kumar-9979b1292}{\faLinkedin\ LinkedIn} ~
  \href{https://github.com/rakshit432}{\faGithub\ GitHub}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading{Birla Institute of Technology, Mesra}{Sept 2023 – Present}{B.Tech in Computer Science and Engineering}{CGPA: \textbf{8.03 / 10.0}}
  \resumeSubheading{Shivam Convent, Patna}{2020 – 2022}{Senior Secondary (XII), CBSE}{82.4\%}
  \resumeSubheading{Open Minds – A Birla School}{2009 – 2020}{Secondary (X), CBSE}{93\%}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{\href{https://blogonspot.vercel.app}{BlogOnSpot — MERN Blogging Platform}} $|$ Vercel, Render}{}
\resumeItemListStart
  \resumeItem{Developed full-stack platform for 200+ users with JWT auth, admin moderation, and secure CRUD operations.}
  \resumeItem{Integrated AI-powered blog summarization and plagiarism detection, reducing review time by 40\%.}
  \resumeItem{Implemented hover-based content previews and dashboard analytics improving engagement by 25\%.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{\href{https://resumebuilder-frontend-6gjz.onrender.com/}{Resume Builder — MERN Application}} $|$ React, Express, MongoDB}{}
\resumeItemListStart
  \resumeItem{Built resume creation tool enabling users to design and export resumes with a responsive, Tailwind-based UI.}
  \resumeItem{Added JWT-based authentication, multi-resume management, and AI suggestions for 10+ skill categories.}
  \resumeItem{Achieved 30\% faster data handling through optimized MongoDB schema and API structure.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Mediversal — Appointment Booking System (In Progress)} $|$ MERN Stack}{}
\resumeItemListStart
  \resumeItem{Architected appointment platform supporting 3 roles (Admin, Doctor, Patient) with real-time schedule sync.}
  \resumeItem{Improved backend efficiency by 20\% using modular Express routing and middleware-based validation.}
  \resumeItem{Planned integration of payment gateway and analytics dashboard for 50+ expected active users.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item \textbf{Languages:} Java, C++, Python, SQL, JavaScript \\
\item \textbf{Web Technologies:} React.js, Node.js, Express.js, MongoDB, Tailwind CSS, REST APIs \\
\item \textbf{Tools \& Platforms:} Git, GitHub, VS Code, Linux, Jupyter Notebook \\
\item \textbf{Libraries:} NumPy, Pandas \\
\item \textbf{CS Concepts:} OOP, DSA, DBMS, Operating Systems
}
\end{itemize}

%-----------EXTRACURRICULAR-----------
\section{EXTRACURRICULAR}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{Acted in 4+ college drama productions; directed a stage monologue viewed by 300+ attendees.}
    \resumeItem{Organized and promoted 2+ NSS technical drives, increasing event turnout by 35\%.}
    \resumeItem{Volunteered for BIT Mesra’s flagship fests — Bitotsav \& Pantheon — managing 10+ sponsors.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------POSITIONS OF RESPONSIBILITY-----------
\section{POSITIONS OF RESPONSIBILITY}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{\textbf{Cyber \& Web Lead — NSS Executive Body:} Led team of 6 in building website modules and event dashboards.}
    \resumeItem{\textbf{Sponsorship Lead — Finance Club:} Managed 15+ sponsor communications, securing ₹30K in funding.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{Solved 700+ problems across LeetCode, Codeforces, and GFG — improving accuracy by 20\% in 3 months.}
    \resumeItem{Scored 97.83 percentile in JEE Mains among 1.5M+ candidates nationwide.}
    \resumeItem{Awarded “All-Rounder of the Year” for excellence in academics, leadership, and arts.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
